Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
PCA pipeline example runs across page boundaries; make it float
There are more cases where this happens, but this is the longest
snippet.

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
As an example, the following snippet illustrates how to create a complex worflow
computing both linear PCA and kernel PCA components on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selecting the 10 best of those features according to an ANOVA test
and then feeding them to an $\ell_2$-regularized logistic regression model:
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression

@@

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}

>>>>

\texttt{Pipeline} and \texttt{FeatureUnion} can be
combined to create complex and nested workflows.
Figure~\ref{union+pipeline} illustrates how to create a complex estimator
that computes both linear PCA and kernel PCA features on \texttt{X\_train}
(through a \texttt{FeatureUnion}),
selects the 10 best features in the combination according to an ANOVA test
and feeds those to an $\ell_2$-regularized logistic regression model.

\begin{figure}[h]
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA
from sklearn.feature_selection import SelectKBest
from sklearn.linear_model import LogisticRegression

@@

Pipeline([("feat_union", fu),
          ("feat_sel", SelectKBest(k=10)),
          ("log_reg", LogisticRegression(penalty="l2"))
]).fit(X_train, y_train).predict(X_test)
\end{pythoncode}
\caption{Combined use of \texttt{Pipeline} and \texttt{FeatureUnion}.}
\label{union+pipeline}
\end{figure}
